\documentclass[]{cv-style} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\begin{document}

\header{Brian}{Mitchell}{Senior Frontend Software Engineer and Web Developer}
\lastupdated

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
\small{Minneapolis, MN USA}
~
+1 (612) 356-4590
~
\href{mailto:brian@brianm.me}{brian@brianm.me}
~
\href{https://brianm.me}{https://brianm.me}
\href{https://github.com/BrianMitchL}{github.com/BrianMitchL}
\section{skills}
TypeScript, JavaScript
React, Vue, Svelte
TanStack Query
react-table
Redux
styled-components
PostCSS
Jest, Vitest
Testing Library
Cypress, Puppeteer
\code{git}
Webpack, Vite
Rollup, Node.js
Ruby on Rails
Next.js, NestJS
Eleventy, Jekyll
HTML5, SCSS
Bash, GitHub Actions
Linux, Open Source
\LaTeX
\section{interests}
tech meetups
frontend development
scripting
lighting design
podcasting
alpine skiing
cycling
urbanism
music
\end{aside}


%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}

%\begin{entrylist}
%
%%------------------------------------------------
%
%\entry
%{2016--Now}
%{Company Name}
%{City, State}
%{\jobtitle[Time]{Position} \\
%Description}
% Detailed achievements:
%  \begin{itemize}
%    \item Achievement 1. 
%    \item Achievement 2.
%    \item Achievement 3.
%  \end{itemize}}
%
%%------------------------------------------------
%
%\end{entrylist}

\begin{entrylist}

%------------------------------------------------

\entry
{2022--Now}
{soona}
{Minneapolis, Minnesota}
{\jobtitle[June 2022-Present]{Senior Software Engineer}
\begin{itemize}
    \item[--] Championed and contributed to modernization and decoupling of frontend codebase through Rails, bundler, and frontend updates.
    \item[--] Rebuilt chat feature to improve stability and observability
\end{itemize}}

\entry
{2021--2022}
{Level2 Health}
{Minnetonka, Minnesota}
{\jobtitle[April 2021-May 2022]{Senior Frontend Engineer}
\begin{itemize}
    \item[--] Wrote the state management and data flow of a Twilio chat interface.
    \item[--] Led the architecture and rebuild of the Coaching Portal React app.
\end{itemize}}

\entry
{2016--2021}
{C.H. Robinson}
{Eden Prairie, Minnesota}
{\jobtitle[March 2021-April 2021]{Senior Software Engineer}

\jobtitle[August 2019-March 2021]{Software Engineer III}
\begin{itemize}
    \item[--] Led the frontend development of customer facing analytics.
    \item[--] Worked with leaders on the customer solutions teams to create and document technical patterns.
    \item[--] Lead technical maintainer of a hubot chatbot running in Slack.
    \item[--] Advocated for React Testing Library and modernizing tooling.
    \item[--] Led the rewrite of data tables to be faster, more reusable, and with a smaller overhead using the hooks-based react-table.
\end{itemize}

\jobtitle[January 2018-August 2019]{Software Engineer II}
\begin{itemize}
    \item[--] Wrote a React library for managing events with Adobe Analytics.
    \item[--] Created a multi-source user authentication and impersonation flow.
    \item[--] Mentored and advocated for using React hooks and Testing Library.
    \item[--] Built performant and animated charting and table components.
    \item[--] Led development and publishing for the \href{https://engineering.chrobinson.com}{Engineering Blog}.
\end{itemize}

\jobtitle[November 2016-January 2018]{Software Engineer I}
\begin{itemize}
    \item[--] Built new widgets and lead major refactoring for a customer analytics tool to add powerful dynamic data filtering application-wide.
    \item[--] Designed new and rewrote screens in an animation-focused data visualization tool for lobby displays leveraging D3 and Bing Maps.
\end{itemize}}

%------------------------------------------------

\entry
{2015}
{C.H. Robinson}
{Eden Prairie, Minnesota}
{\jobtitle[May 2015-August 2015]{IT Intern} \\
Developed an interactive lobby display illustrating shipments on a world map, built with web technologies for touch-driven hardware.}

%------------------------------------------------

\entry
{2014--2015}
{University of Minnesota, Morris}
{Morris, Minnesota}
{\jobtitle[August 2014-May 2015]{System Administrator} \\
Upgraded Fedora workstation management with Puppet, LDAP, and NFS.}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}

%------------------------------------------------

\entry
{2012--2016}
{Bachelor of Arts {\normalfont Computer Science}}
{University of Minnesota, Morris}
{\small{Focused on Web Development and interpreted languages}}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	OTHER SECTION
%----------------------------------------------------------------------------------------

\section{other}

\begin{entrylist}

%------------------------------------------------

\entry
{2019--Now}
{Co-Organizer {\normalfont \href{https://javascriptmn.com}{JavaScriptMN}}}
{Minneapolis, Minnesota}
{A monthly meetup for JavaScript and related technologies.}

%------------------------------------------------


\entry
{2022--Now}
{Board Member {\normalfont \href{https://streets.mn}{Streets.mn}}}
{Minnesota}
{Transportation and land use blog and non-profit organization.}

%------------------------------------------------

\end{entrylist}

\end{document}