\documentclass[]{cv-style} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\sethyphenation{english}{} % Add words between the {} to avoid them to be cut

\usepackage{fontawesome} % on macOS, you need to install FontAwesome.otf in Font Book

\begin{document}

\header{Brian}{Mitchell}
\lastupdated

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{contact}
5645 Harriet Ave
Minneapolis, MN 55419
United States
~
+1 (612) 356-4590
~
\href{mailto:bman4789@gmail.com}{bman4789@gmail.com}
\href{https://brianm.me}{https://brianm.me}
\href{https://github.com/BrianMitchL}{\textcolor{darkgray}{\faicon{github} }github/BrianMitchL}
\href{https://twitter.com/BrianMitchL}{\textcolor{twitter}{\faicon{twitter} }@BrianMitchL}
\section{languages}
JavaScript, Python
Swift, C, Java
CSS3 \& HTML5
Bash, \LaTeX
\section{frameworks \& tools}
AngularJS, D3
Node.js, Jekyll
Puppet, MongoDB
Travis CI, Docker
\section{software}
\textcolor{gray}{\texttt{git}}, WebStorm
PyCharm, Eclipse
Xcode, Final Cut Pro X
Logic Pro X
\section{operating systems}
macOS, Fedora
REHL 7, Windows
\section{other}
pair programming
agile methodologies
communication skills
organization
lighting design
EOS family consoles
\end{aside}

%----------------------------------------------------------------------------------------
%	SUMMARY SECTION
%----------------------------------------------------------------------------------------
\vspace{0.2cm}
\section{summary}

A skilled and knowledgeable developer proficient in web development and *nix systems. Detail oriented and strong interpersonal skills. Educated with a Bachelor's degree in Computer Science.

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}

%\begin{entrylist}
%
%%------------------------------------------------
%
%\entry
%{2016--Now}
%{Company Name}
%{City, State}
%{\jobtitle{Position} \\
%Description}
% Detailed achievements:
%  \begin{itemize}
%    \item Achievement 1. 
%    \item Achievement 2.
%    \item Achievement 3.
%  \end{itemize}}
%
%%------------------------------------------------
%
%\end{entrylist}

\begin{entrylist}

\entry
{2016--Now}
{C.H. Robinson}
{Eden Prairie, Minnesota}
{\jobtitle{Business Intelligence Developer - Enterprise Data Warehouse} \\
Implementing and designing the front end of several reporting and analytical based web applications. Tools: JavaScript, AngularJS, webpack, D3, Highcharts, Bing Maps.}

%------------------------------------------------

\entry
{2015--Now}
{Independent Work}
{\href{https://github.com/BrianMitchL/weatherBot}{https://github.com/BrianMitchL/weatherBot}}
{\jobtitle{weatherBot} \\
A Twitter bot for weather producing weather forecasts and current conditions. Written in Python and deployed with Docker. Live bot at \href{https://twitter.com/WeatherByBrian}{@WeatherByBrian}.}

%------------------------------------------------

\entry
{2015}
{C.H. Robinson}
{Eden Prairie, Minnesota}
{\jobtitle{IT Intern} \\
Developed an interactive lobby display illustrating active shipments on an animated world map, implemented with web technologies for touch-driven hardware.}

%------------------------------------------------

\entry
{2014--2015}
{University of Minnesota, Morris}
{Morris, Minnesota}
{\jobtitle{System Administrator} \\
Improved efficiency of and supported the computer science labs. The labs consisted of 30 Fedora workstations managed by Puppet, and using LDAP and NFS.}

%------------------------------------------------

\entry
{2014}
{Info-Link, Inc.}
{Morris, Minnesota}
{\jobtitle{IT Specialist} \\
Supported customers, repaired and maintained internal systems. Serviced and installed radios in homes, businesses, and various broadcasting towers.}

%------------------------------------------------

\entry
{2012--2016}
{University of Minnesota, Morris}
{Morris, Minnesota}
{\jobtitle{Student Center Tech Crew} (\jobtitle{Lighting Lead} 2014-2015 and Spring 2016) \\
Led work calls and designed, set-­up, and operated sound and lighting for events.}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\vspace{-0.2cm}
\section{education}

\begin{entrylist}

%------------------------------------------------

\entry
{2012--2016}
{Bachelor of Arts {\normalfont Computer Science}}
{University of Minnesota, Morris}
{\emph{Coursework}: \footnotesize{Robotics (C), Network Administration Practicum with an Emphasis on Directory Services, Models of Computing Systems (Bash, Ruby, C, Java), Human-Computer Interface Design (JavaScript), Algorithms and Computability (Java), Software Design and Development (JavaScript), Ethical and Social Implications of Technology, Data Structures (Java), Digital Media Computation (Python), Foundations of Computer Science, Calculus I--II, Statistical Methods}}

\entry
{2015}
{Study Abroad}
{Danish Institute for Study Abroad, Copenhagen, Denmark}
{\emph{Coursework}: \footnotesize{Artificial Intelligence, Danish Language I--II, Sustainable Development in Northern Europe}}
%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	OTHER SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{other}

\begin{entrylist}

%------------------------------------------------

\entry
{2016}
{Oral Presentation {\normalfont \emph{with distinction}}}
{Computer Science Senior Seminar Conference, Morris, Minnesota}
{My survey analysis, \emph{Aggregating Information Based on Geolocated Twitter Data}.}

%------------------------------------------------

\entry
{2016}
{CarlHacks Hackathon}
{Carleton College, Northfield, Minnesota}
{Wrote a beats-per-minute tracking iOS application in Swift.}

%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

%\section{honors \& awards}
%
%\begin{entrylist}
%
%%------------------------------------------------
%
%\entry
%{year}
%{what}
%{Where, where}
%{description}
%
%%------------------------------------------------
%
%\end{entrylist}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{interests}

\textbf{professional:} web development and design, software development, scripting, iOS development, lighting design, theatrical electrician \textbf{personal:} podcasting, alpine skiing, music

\end{document}